% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\documentclass[withoutpreface,bwprint]{cumcmthesis} 
\input{Misc/preamble.tex}
%以上为格式规定与包的引用，勿动。以下为正文内容，从标题开始

%标题
\title{Title}
\usepackage{fontspec}
\setmainfont{Arial}


\renewcommand{\headrulewidth}{0pt} % 不显示页眉线
\renewcommand{\footrulewidth}{0pt} % 不显示页脚线\left( 
\begin{document}
 \maketitle
%英文摘要
\renewcommand{\abstractname}{Abstract}
\renewcommand{\keywords}{\textbf{Keywords：}}
\begin{abstract}
\begin{spacing}{1.6}

%英文摘要内容
\end{spacing}
\noindent\keywords{Frequency Selective Surface\quad Polarization Insensitivity\quad Three-layer Composite Structure}
\end{abstract}

%目录（前三行为目录格式调整）
%\cftsetindents{section}{0em}{2em}
%\cftsetindents{subsection}{2em}{3em}
%\cftsetindents{subsubsection}{4em}{4em}
% \newpage
% \tableofcontents
 \newpage

%以下部分为正文内容
\input{1.Introduction/introduction.tex}
%theory
\input{2.Mathematical_model/mathematical_model.tex} 
% method
\input{3.Discussion/discussion.tex}
%result
\input{4.Results/results.tex}
%analyse
%\input{5.Conclusion/conclusion.tex}
%Conclusion

%参考文献
\newpage
\begin{thebibliography}{99}

\bibitem{ref1} Moen, E., Bannon, D., Kudo, T., Graf, W., Covert, M., \& Van Valen, D. (2019). Deep learning for cellular image analysis. Nature Methods, 16(12), 1233-1246. https://doi.org/10.1038/s41592-019-0403-1

\bibitem{ref2}Moen, E., Bannon, D., Kudo, T., Graf, W., Covert, M., \& Van Valen, D. (2019). Deep learning for cellular image analysis. Nature Methods, 16, 1233-1246. Available at: https://www.nature.com/articles/s41592-019-0403-1.

\bibitem{ref3}Nash, W., Drummond, T. \& Birbilis, N. (2018). A review of deep learning in the study of materials degradation. npj Materials Degradation, 2, Article number: 37. Available at: https://www.nature.com/articles/s41529-018-0058-x

\bibitem{ref4}Nash, W., Drummond, T. \& Birbilis, N. (2018). A review of deep learning in the study of materials degradation. npj Materials Degradation, 2(1). Available at: https://www.nature.com/articles/s41529-018-0058-x 

%\bibitem{2} \url{WEBSITE}
\end{thebibliography}

%附录
% Appendix
%\appendix
%\pagenumbering{roman}
%\input{6.Appendix/appendix_A.tex}
%\input{6.Appendix/appendix_B.tex}
%\input{6.Appendix/appendix_C.tex}

%Example部分用于存放各种样例
% \newpage
% \input{Example/example.tex}

\end{document} 